### 2020-03-23 papers.tex
Add papers arriving by the end of the *real* preceding proceedings weekend

@@

>>>>

	{SIGBOVIK_2020_paper_11}

@@

	{Is this the longest Chess game?}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chesses, chessing, G.\@ K.\@ Chesterton}
	{SIGBOVIK_2020_paper_28}
	{Verified proof of P=NP in the Silence theorem prover language}
	{Matias Scharager}
	{Keywords: soundness, P=NP, theorem prover, Silence, programming language theory, type theory}
	{SIGBOVIK_2020_paper_29}
	{What is the best game console?: A free-market--based approach}
	{Dr.\@ Tom ``I Only Write Chess Papers Now'' Murphy VII Ph.D.}
	{Keywords: invisible hand, handheld console, minimum of 3 keywords}
	{SIGBOVIK_2020_paper_30}
